\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-06-04 doc/sw-publication-policy-cfhtls.tex

Please email the \sw PIs at \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com} if you have any
ideas for further \sw series or related papers.

>>>>

\subsection{Additional \sw series or related papers}
Please email the \sw PIs at \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com} if you have any
ideas for further \sw series or related papers.

### 2014-06-04 doc/sw-system.tex
Stage 2 results now match Anu's

We define the following properties of the crowd, as characterised by their
agents, and plot the distributions of their logarithms in
\Fref{fig:crowd:cornerplot}. 
%
\begin{description}
%
\item{\noindent\bf ``Effort:''} The number of test images, $\effort$, classified by a
volunteer. In stage 1, the mean effort per agent was 263; in the shorter stage
2 it was 81.
%
\item{\noindent\bf ``Experience:''} The number of training images, $\experience$,
classified by a volunteer. In stage 1, the mean experience per agent was 29;
in stage 2 (where the training image fequency was set higher) it was 34.
%
\item{\noindent\bf ``Skill:''} The expectation value of the information gain, $\skill$
should  the next subject classified have lens probability 0.5
\Aref{appendix:swap},  in bits. Random classifiers have $\skill = 0.0$,
perfect classifiers have $\skill = 1.0$. All agents start with $\skill = 0.0$;
this increases as training subjects are classified, and the agent's estimates
of its confusion matrix elements improve. In stage 1, the mean skill per agent
was 0.04 bits; in  stage 2 it was 0.05.
%
\item{\noindent\bf ``Contribution:''} The integrated skill over a volunteer's test
subject classification history, and represents the total  contribution to the
project that volunteer (see the appendix for more discussion of this
quantity). In stage 1, the mean contribution per agent was 34.3 bits; in 
stage 2 it was 33.5.
%
\item{\noindent\bf ``Information:''} The total information $\information$ generated by
the  agent during the volunteer's classification activity. This quantity
depends on the value of each subject's lens probability when that subject was 
presented to the volunteer (\Aref{appendix:swap}), and so there is an element
of luck involved with this quantity: if you never see a high probability
subject, it's hard to generate a large amount of information. You make your
own luck by classifying more subjects.
%
\end{description}

The leftmost column of \Fref{fig:crowd:cornerplot} shows how the last four of
these properties depends on the effort expended by the volunteers. We see that
experience is strongly correlated with effort (as training images are
presented throughout each stage, albeit at decreasing frequency), and that
this is also true for skill. In the second row of \Fref{fig:crowd:cornerplot}
we see that while skills of greater than 0.1 can be attained after just a few
training images, most agents of such low experience have significantly lower
skill. The volunteers in question only classify a few subjects before leaving.
However, at high values of experience and effort, the skill is \emph{always
high}. There seem to be very few agents logging large numbers of
classifications at low skill (although there are one or two exceptions). Most
high effort ``super-users'' have high skill. These two properties are
reflected in both the contributions these volunteers make (third row) and the
information they generate (fourth row).

@@

However, it is not the case that only these small groups were capable of
making this large contribution: 9097 volunteers were ``experienced'' in that
they had all classified at least 10 training images; the 375 highest
contributing volunteers make up just 4\% of this experienced volunteer pool.
The cumulative distribution of agent skill is shown in
\Fref{fig:crowd:cumulskillplot}: these distributions are significantly broader
than the corresponding distributions of agent contribution in 
\Fref{fig:crowd:cumulplot}. The most skilled 20\% of agents possess only  79\%
of the skill at stage 1, and 77\% at stage 2. The inexperienced volunteers
also possess a significant fraction of the skill: the most skillful 20\% of
experienced volunteers (1820 people)  possess just 43\% of the total skill.
The level of contribution made at \sw by experienced volunteers is largely a
matter of choice (or perhaps, availability of time!).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/early_vs_final_skill.png}
\caption{Predictability of final skill from early skill (after 10 training
classifications) in stage 1 agents. The dashed lines enclose 649 agents with
early skill greater than 0.1 
who retain final skill of greater than 0.05.}
\label{fig:crowd:skillprediction}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Having seen the importance of the high skill volunteers at both stage 1 and
stage 2, we might ask, can we predict agent skill after, say, the volunteer
has experienced 10 training subjects? In \Fref{fig:crowd:skillprediction} we
plot this ``early skill'' against final skill, for all experienced stage 1
volunteers. The majority of the crowd shows little correlation, but at the
high early skill end, some predictability appears. The 649 experienced  stage
1 volunteers who had early skill greater than 0.1 went on to attain a mean
final skill of 0.22, with 97\% remaining at skill 0.05 or higher. This
suggests that it might be worth tracking volunteers' skill as a project
progresses, in order to encourage those showing an aptitude for the task to
take part in the more difficult activities, such as stage 2 refinement.

\Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
information generated in both stage 1 and 2 of the CFHTLS project, with the
total numbers of agents and subjects for comparison. These numbers allow us to
quantify the efficiency of the system. The contribution per classification is
defined in terms of a hypothetical subject with lens probability of 0.5; one
bit of information is needed to update such a subject's lens probability to
either zero or one. This means that a maximally complete classification stage
would yield a total contribution (summed over all agents) equal to the number
of subjects. The ratio of this hypthetical optimum to the actual total
contribution is therefore a measure of the stage's inefficiency. We find our
inefficiency (by dividing column 2 by column 3) to be 33\% and 17\% in stage 1
and 2 respectively. In stage 1, this inefficiency is due to the daily
processing: we were not able to retire subjects fast enough, and so they,
remained in the system, being over-classified. Only 3705704 classifications
were needed to retire all the subjects: the ratio of this to the total number
made is 34\%. (The remaining 1\% is due to not all subjects being classified
to 1 or 0 probability.) At stage 2, we did not retire any subjects at all; the
inefficiency in this case was by design, to give everyone a chance to
appreciate what they had found together!

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}
\begin{center}
\caption{Total crowd and subject sample properties from the CFHTLS project.}
\label{tab:crowd:contributions}
\begin{tabular}{cccccccc}
  \hline
  \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
                 & $\Ns$    & $\sum_k^{\Nv} \contribution_k$ (bits) & $\Nv$  & $\sum_k^{\Nv} \skill_k$ (bits) & $\sum_k^{\Nv} \thiseffort$ & $\Ncands$  & $\sum_j^{\Ns}\sum_k^{\Nv} \information_{j,k}$ (bits) \\
  \hline 
            1    & $427064$ & $1291997.4$ & $36929$ & $1469.9$ & $10768759$ & $3367$ & $91110.7$ \\
            2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $91$ &  $1641.9$ \\
  \hline \hline
\end{tabular}
\medskip\\
\end{center}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

We define the following properties of the crowd, as characterised by their
agents, and plot the distributions of their logarithms in
\Fref{fig:crowd:cornerplot}. 
%
\begin{description}
%
\item{\noindent\bf ``Effort:''} The number of test images, $\effort$, classified by a
volunteer. In stage 1, the mean effort per agent was 263; in the shorter stage
2 it was 81.
%
\item{\noindent\bf ``Experience:''} The number of training images, $\experience$,
classified by a volunteer. In stage 1, the mean experience per agent was 29;
in stage 2 (where the training image fequency was set higher) it was 34.
%
\item{\noindent\bf ``Skill:''} The expectation value of the information gain, $\skill$
should  the next subject classified have lens probability 0.5
\Aref{appendix:swap},  in bits. Random classifiers have $\skill = 0.0$,
perfect classifiers have $\skill = 1.0$. All agents start with $\skill = 0.0$;
this increases as training subjects are classified, and the agent's estimates
of its confusion matrix elements improve. In stage 1, the mean skill per agent
was 0.04 bits; in  stage 2 it was 0.05.
%
\item{\noindent\bf ``Contribution:''} The integrated skill over a volunteer's test
subject classification history, and represents the total  contribution to the
project that volunteer (see the appendix for more discussion of this
quantity). In stage 1, the mean contribution per agent was 34.9 bits; in 
stage 2 it was 33.5.
%
\item{\noindent\bf ``Information:''} The total information $\information$ generated by
the  agent during the volunteer's classification activity. This quantity
depends on the value of each subject's lens probability when that subject was 
presented to the volunteer (\Aref{appendix:swap}), and so there is an element
of luck involved with this quantity: if you never see a high probability
subject, it's hard to generate a large amount of information. You make your
own luck by classifying more subjects.
%
\end{description}

The leftmost column of \Fref{fig:crowd:cornerplot} shows how the last four of
these properties depends on the effort expended by the volunteers. We see that
experience is strongly correlated with effort (as training images are
presented throughout each stage, albeit at decreasing frequency), and that
this is also true for skill. In the second row of \Fref{fig:crowd:cornerplot}
we see that while skills of greater than 0.1 can be attained after just a few
training images, most agents of such low experience have significantly lower
skill. The volunteers in question only classify a few subjects before leaving.
However, at high values of experience and effort, the skill is \emph{always
high}. There seem to be very few agents logging large numbers of
classifications at low skill (although there are one or two exceptions): almost
all high effort ``super-users'' have high skill. These two properties are
reflected in both the contributions these volunteers make (third row) and the
information they generate (fourth row).

@@

However, it is not the case that only these small groups were capable of
making this large contribution: 9118 volunteers were ``experienced'' in that
they had all classified at least 10 training images; the 375 highest
contributing volunteers make up just 4\% of this experienced volunteer pool.
The cumulative distribution of agent skill is shown in
\Fref{fig:crowd:cumulskillplot}: these distributions are significantly broader
than the corresponding distributions of agent contribution in 
\Fref{fig:crowd:cumulplot}. The most skilled 20\% of agents possess only  79\%
of the skill at stage 1, and 77\% at stage 2. The inexperienced volunteers
also possess a significant fraction of the skill: the most skillful 20\% of
experienced volunteers (1824 people)  possess just 43\% of the total skill.
The level of contribution made at \sw by experienced volunteers is largely a
matter of choice (or perhaps, availability of time!).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/early_vs_final_skill.png}
\caption{Predictability of final skill from early skill (after 10 training
classifications) in stage 1 agents. The dashed lines enclose 649 agents with
early skill greater than 0.1 
who retain final skill of greater than 0.05. Point size is proportional to
contribution (plus a constant).}
\label{fig:crowd:skillprediction}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Having seen the importance of the high skill volunteers at both stage 1 and
stage 2, we might ask, can we predict agent skill after, say, the volunteer
has experienced 10 training subjects? In \Fref{fig:crowd:skillprediction} we
plot this ``early skill'' against final skill, for all experienced stage 1
volunteers. The majority of the crowd shows little correlation, but at the
high early skill end, some predictability appears. The 649 experienced  stage
1 volunteers who had early skill greater than 0.1 went on to attain a mean
final skill of 0.22, with 97\% remaining at skill 0.05 or higher. This
suggests that it might be worth tracking volunteers' skill as a project
progresses, in order to encourage those showing an aptitude for the task to
take part in the more difficult activities, such as stage 2 refinement.
However, this would not have done a very good job at identifying the 
volunteers who went on to make the largest contributions: the point size in 
\Fref{fig:crowd:skillprediction} is proportional to contribution (plus a constant):
many of the highest contributors showed relatively low skill early on.

\Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
information generated in both stage 1 and 2 of the CFHTLS project, with the
total numbers of agents and subjects for comparison. These numbers allow us to
quantify the efficiency of the system. The contribution per classification is
defined in terms of a hypothetical subject with lens probability of 0.5; one
bit of information is needed to update such a subject's lens probability to
either zero or one. This means that a maximally complete classification stage
would yield a total contribution (summed over all agents) equal to the number
of subjects. The ratio of this hypthetical optimum to the actual total
contribution is therefore a measure of the stage's inefficiency. We find our
inefficiency (by dividing column 2 by column 3) to be 33\% and 17\% in stage 1
and 2 respectively. In stage 1, this inefficiency is due to the daily
processing: we were not able to retire subjects fast enough, and so they,
remained in the system, being over-classified. Only 3705745 classifications
were needed to retire all the subjects: the ratio of this to the total number
made is 34\%. (The remaining 1\% is due to not all subjects being classified
to 1 or 0 probability.) At stage 2, we did not retire any subjects at all; the
inefficiency in this case was by design, to give everyone a chance to
appreciate what they had found together!

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}
\begin{center}
\caption{Total crowd and subject sample properties from the CFHTLS project.}
\label{tab:crowd:contributions}
\begin{tabular}{cccccccc}
  \hline
  \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
                 & $\Ns$    & $\sum_k^{\Nv} \contribution_k$ (bits) & $\Nv$  & $\sum_k^{\Nv} \skill_k$ (bits) & $\sum_k^{\Nv} \thiseffort$ & $\Ncands$  & $\sum_j^{\Ns}\sum_k^{\Nv} \information_{j,k}$ (bits) \\
  \hline 
            1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3368$ & $91122.6$ \\
            2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $90$ &  $1640.4$ \\
  \hline \hline
\end{tabular}
\medskip\\
\end{center}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
